Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-17 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10. The experiments were performed with a predefined time out of $240$ minutes.

\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, \textit{RQ2} (performance) How do the software verifiers compare to each other?, and \textit{RQ3} how does our formal synthesis tool compare to a specialized simulation tool?

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. %Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W). The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. %However, if it is removed this time out limitation from CPAchecker, the verifier is able to solve the optimization in $44.97$ hours. 
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EQ2} and \textit{EQ3}.

@@

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). Particularly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling. The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value. However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation. Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.

@@

\textbf{Conclusion.} Summarizing, our synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage. In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).

%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

@@

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparison.

>>>>

\noindent \textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10. The experiments were performed with a predefined time out of $240$ minutes.

\noindent \textbf{Objectives.} Our evaluation aims to answer three experimental questions: 
\textit{EQ1} \textbf{(soundness)} Does our automated synthesis approach provide correct results?, 
\textit{EQ2} \textbf{(performance)} How do the software verifiers compare to each other?, and 
\textit{EQ3} \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?

\noindent \textbf{Results.} CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. 
Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EQ2} and \textit{EQ3}.

@@

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling. The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value. However, there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because of the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation. \textcolor{red}{This sentence is hard to understand... try to break into smaller sentences...Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.} These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.

@@

\noindent \textbf{Threats to validity.} We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained, and it allows a simulation-verification comparison.

\noindent \textbf{Conclusion.} Summarizing, our synthesis tool is capable of presenting a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

@@
